---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# A Shiny app to calculate RIV points

This RShiny app calculates RIV points according to [Dean's Measure No. 18/2024](https://www.frov.jcu.cz/images/FROV/fakulta/uredni-deska/opatreni-dekana/2024/Measure_of_Dean_18-2024.pdf). The app uses the *Clarivate Journal Citation Report* data to calculate the RIV points for scientific outputs such as journal articles. The app is designed to be used by researchers and research institutions in the Czech Republic.


## Repository structure

- The **raw data** can be found in the `data/` directory.
- The `www/` directory holds all logo files in `.png` format.
- `calc.xlsx` is just a test calculation and not part of the app.


## Usage

- to add new *Clarivate Journal Citation Report* data, add the `.xlsx` file to the `data/` directory. Also, the dropdown menu (`input$dataset`) must be updated by adding the dataset name as additional `selectInput` option in the `ui.R` file.
- version updates shall be described in `NEWS.md` and the updated version number added to `DESCRIPTION` from where it is queried in the `app.R` file and displayed in the UI automatically.


```{r}
sessionInfo()
```
